Road Accident Prediction in Time and Space

### 2019-04-22 paper/paper.tex
Paper: reorganization

\section{Introduction}
\subsection{Context}
According to the World report on road traffic injury prevention, 2004, more than one million people die every year from car accidents and dozens of millions of people are being injured\cite{Peden2004}. In this report, the World Health Organization also describe road traffic systems as “the most complex and the most dangerous system with which people have to deal every day”. This issue is all the more important that the number of accidents is forecast to continue rising. In the last decade, Big Data Analytics has been emerging \cite{Gandomi2015}, allowing scientists to handle a very large amount of data, but also complex and heterogeneous data, in order to extract useful insights from it. In the context of accident prediction, Big Data Analytics could provide insights on the conditions leading to an increased risk of road accidents that could then be used to develop traffic-related policies and prevention operations. Our contributions include: 
\begin{itemize}
\item a demonstration of how simple and easily available datasets can be assembled to obtain meaningful features for road accident prediction,
\item a comparison of three different machine learning algorithm dealing with data imbalance in the context of road accident prediction,
\item the implementation of Balanced Random Forest introduced by Chen et al.\cite{Chen2004} in Apache Spark for efficient distributed training. 
\end{itemize}
All the source code used is publicly available on Github under the MIT license.\footnote{https://github.com/GTimothee/accident-prediction-montreal}

need to be extended:
  how our dataset is bigger because 6 years and precise because road segments

@@

\section{Methods}
\subsection{Choosing a Big Data framework: Apache Spark or Dask}
According to Dask’s official website, “Dask is a flexible library for parallel computing in Python” \cite{dask}. Apache Spark, on the other hand, describes itself as “a fast and general-purpose cluster computing system” \cite{spark}. Both of them are accepted tools with wide supporting community, even though Apache Spark is a bigger and older project. Although we almost exclusively used Apache Spark’s Python API (called “pySpark”) in this study, we started our experiment using Dask. Some advantages of Dask over Spark made us chose it for our analysis in the first place; For example, Dask “is developed in coordination with […] projects like Numpy, Pandas and Scikit-Learn” \cite{dask}, all widely used Python packages in machine-learning and data science. It is also admitted that Dask is lighter than Spark and designed to be more flexible in terms of applications and algorithms. However, we found ourselves writing a lot more code using Dask than Spark for the same result. Spark map-reduce-based interface is very handy and allows easier processing of datasets. For all these reasons we found out that Spark fitted our needs best and we switched to it at an early time of the study.

@@

@@

\subsection{Future work}
We believe better performances could be reached by adding more features from other datasets. For the city of Montreal, we identified two particularly interesting datasets: a dataset with the location and dates of construction work on roads, and a dataset with the population density. These datasets might not be as easily available for over areas, but for Montreal, it could improve performances. Also, the solar elevation and solar azimuth could easily be added without the need for another dataset. These features have been used successfully in road accident prediction in previous experiments.

@@

We acknowledge Compute Canada for giving us access to the cluster.

>>>>

\section{Introduction}
According to the World report on road traffic injury prevention, 2004, more than one million people die every year from car accidents and dozens of millions of people are being injured\cite{Peden2004}. In this report, the World Health Organization also describe road traffic systems as “the most complex and the most dangerous system with which people have to deal every day”. This issue is all the more important that the number of accidents is forecast to continue rising. In the last decade, Big Data Analytics has been emerging \cite{Gandomi2015}, allowing scientists to handle a very large amount of data, but also complex and heterogeneous data, in order to extract useful insights from it. In the context of accident prediction, Big Data Analytics could provide insights on the conditions leading to an increased risk of road accidents that could then be used to develop traffic-related policies and prevention operations. Our contributions include: 
\begin{itemize}
\item a demonstration of how simple and easily available datasets can be fused to obtain meaningful features for road accident prediction,
\item the implementation of Balanced Random Forest introduced by Chen et al.\cite{Chen2004} in Apache Spark for efficient distributed training.
\item a comparison of three different machine learning algorithms dealing with data imbalance in the context of road accident prediction,
\item a real-time road accident prediction model for the island of Montreal with good performances
\end{itemize}
All the source code used is publicly available on Github under the MIT license.\footnote{https://github.com/GTimothee/accident-prediction-montreal}

\subsection{Need to be extended, some ideas:}

  As compared to previous studies we have a much bigger dataset of more than a hundred thousands accidents and while other recent studies predict the risk  of an accident in large space area of several square kilometers, we try to predict the occurence of an accident in road segments of a few hundred meters.

@@

\section{Datasets fusing}
\subsection{Choosing a Big Data framework: Apache Spark or Dask}
According to Dask’s official website, “Dask is a flexible library for parallel computing in Python” \cite{dask}. Apache Spark, on the other hand, describes itself as “a fast and general-purpose cluster computing system” \cite{spark}. Both of them are accepted tools with wide supporting community, even though Apache Spark is a bigger and older project. Although we almost exclusively used Apache Spark’s Python API (called “pySpark”) in this study, we started our experiment using Dask. Some advantages of Dask over Spark made us chose it for our analysis in the first place; For example, Dask “is developed in coordination with […] projects like Numpy, Pandas and Scikit-Learn” \cite{dask}, all widely used Python packages in machine-learning and data science. It is also admitted that Dask is lighter than Spark and designed to be more flexible in terms of applications and algorithms. However, we found ourselves writing a lot more code using Dask than Spark for the same result. Spark map-reduce-based interface is very handy and allows easier processing of datasets. For all these reasons we found out that Spark fitted our needs best and we switched to it at an early time of the study.

\section{Model development}

@@

The following table present the statistical characteristic of our features in the traning dataset

@@

Add discussion about why accuracy does not make sense to evaluate performance, and also practical example of what our prediction results means.

\subsection{Future work}
We believe better performances could be reached by adding more features from other datasets. For the city of Montreal, we identified two particularly interesting datasets: a dataset with the location and dates of construction work on roads, and a dataset with the population density. These datasets might not be as easily available for over areas, but for Montreal, it could improve performances. This accident prediction model can be used direcly to know on which road segments accidents are the most likely to happen in a given hour in order to take measure to reduce risk. This would require to put this model into production. The historical climate dataset, would have to be replaced by a weather forecast dataset. The most important feature is the number of accident which happened during the previous year, while this feature help a lot to reach useful prediction performances, it does not help in understanding the characteristics of a road segment which makes it dangerous. A human analysis of these particularly risky road segment could detect patterns that could help to take measure to reduce the number of accident in Montreal. This can also allow to improve our current accident prediction model, if the detected patterns can be used by fusing other datasets.

Add these features:
Also, the solar elevation and solar azimuth could easily be added without the need for another dataset. These features have been used successfully in road accident prediction in previous experiments.

@@

The authors would like to acknowledge Compute Canada for providing access to the computation cluster.
